Verification of concurrent design patterns with data

### 2019-02-19 2018-Arch-pNets/arch-pNets.tex
arch-pNets paper: Reshuffled appendices; merged sections 4 and 5 and added a paragraph to the end of section3

\newcommand{\defn}[1]{Def.~\ref{defn:#1}}
\newcommand{\defntwo}[2]{Defs~\ref{defn:#1} and \ref{defn:#2}}
\newcommand{\fig}[1]{Fig.~\ref{fig:#1}}
\newcommand{\Fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\figs}[2]{Fig.~\ref{fig:#1} and~\ref{fig:#2}}
\newcommand{\tab}[1]{Tab.~\ref{tab:#1}}
\newcommand{\eq}[1]{(\ref{eq:#1})}
\newcommand{\res}[1]{(\ref{res:#1})}
\newcommand{\ex}[1]{Ex.~\ref{ex:#1}}
\newcommand{\exs}[2]{Ex.~\ref{ex:#1} and~\ref{ex:#2}}
\newcommand{\secn}[1]{Sect.~\ref{secn:#1}}
\newcommand{\app}[1]{App.~\ref{secn:#1}}
\newcommand{\rem}[1]{Note~\ref{rem:#1}}
\newcommand{\lem}[1]{Lem.~\ref{lem:#1}}
\newcommand{\cor}[1]{Cor.~\ref{cor:#1}}
\newcommand{\thm}[1]{Th.~\ref{thm:#1}}
\newcommand{\axs}[1]{Ax.~\ref{ax:#1}}
% \newcommand{\ax}[2]{\ref{ax:#1}.\ref{ax:#1:#2}}
\newcommand{\ax}[1]{Ax.~\ref{ax:#1}}
\newcommand{\prop}[1]{Prop.~\ref{prop:#1}}
\newcommand{\alg}[1]{Alg.~\ref{alg:#1}}
\newcommand{\asmp}[1]{Ass.~\ref{asmp:#1}}

@@

@@

The encoding of the interaction model is based on its representation
as a set of connectors. \noteSB{%
%
%%   A legitimate question is whether we actually need to do this,
%%   instead of listing explicitly the individual interactions, then
%%   associating a synchronisation vector to each one of them?  One of
%%   the factors is the encoding pNets$\rightarrow$SAT: is it better to
%%   have more or fewer SVs if the price is additional Boolean variables?
%%   The other factor might be the facility of maximal progress
%%   encoding\mdash TBC.  Traceability.  Anything else?\newline
%%   \hl{UPDATE: Maximal progress encoding requires this!}
%% %
} Indeed, as illustrated by the Failure Monitor architecture in
\fig{schema:ArchFailure:BIP}, each connector can define several
allowed interactions, depending on its hierarchical structure and the
use of synchrons and triggers.

@@

\bigskip
In order to encode the maximal progress priority model, one has to
introduce an additional Boolean variable, for each port, for which we
have introduced one in $\nopri[A, \partition]$.  Intuitively, the
variables introduced above determine whether the original transition
labeled by the port is executed (\true), or rather the corresponding
self-loop, introduced by the encoding (\false).  The new variables
determine whether \emph{there is an original transition labelled by
  $p$ that could be executed from the same state}, \ie[,] with $b_p$
the variable introduced above for the encoding without maximal
progress, $q \goesto{p(\true, b_p)} q'$ iff $\exists q'': q
\goesto{p(b_p)} q''$ with $b_p = \true$ in $\nopri[A, \partition]$.
Then, in the SV guard, we have to check whether \emph{all ports
  leading to $p$ in the causal tree $\tau(x)$ can be fired} (see
\app{transformations}).  If so, then $p$ must be fired, \ie
$p(\false)$ must be blocked.  %% This is pretty much straightforward, but
%% care must be taken when doing this in the general case, since causal
%% interaction trees can get pretty tricky due to $\oplus$ (see
%% \app{trees}).}
%****************************************************************
%****************************************************************

@@

\section{Case study}
\label{secn:case-study}

@@

\subsection{Composition of architectures}
\label{secn:arch:composition}

We now consider a system comprising two components $B_1$ and $B_2$
with the corresponding interfaces $\tuple{V_i, P_i,
  \export[i]}_{i=1,2}$, such that $\listset{\PortFail_i,
  \PortResume_i} \subseteq P_i$, for $i = 1,2$.

Assuming that the associated system requirements comprise the
capability of monitoring the failure events corresponding to ports
$\PortFail_1$ and $\PortFail_2$ of the two components, we would like
to apply two instances of the Failure Monitor architecture.  However,
we impose an additional constraint: only one timer coordinator is
allowed, for example because it must eventually be implemented by a
hardware component.

We consider two architecture instances $A_i = \tuple{\cC_i, V_{A_i},
  P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$, with all their
constituting elements cloned from the Failure Monitor architecture of
the previous examples while substituting each entity $X$ by $X^i$.
For instance, the initialisation of the $\mathit{zone}$ variable is
transformed into $\IntervalInit[1]$ and $\IntervalInit[2]$,
respectively.  The only exception to this cloning procedure are the
sets of coordinating components: $\cC^i = \listset{\NameTimer,
  \NameCtrl^i}$, \ie the $\NameTimer$ component is shared, while
components $\NameCtrl^1$ and $\NameCtrl^2$ are obtained by making two
copies of $\NameCtrl$ as above.

In order to apply both architectures, we must verify that they are
upwards compatible and compute the combined interaction model $\Gamma$
in $A_1 \arcomp A_2 = \tuple{\cC_1 \cup \cC_2, V_{A_1} \cup V_{A_2},
  P_{A_1} \cup P_{A_2}, \export[A_1] \cup \export[A_2], \Gamma}$
(see \defn{arch:composition}).

\todoSBin{Complete this section}

@@

@@

%*********************************************************************
%*********************************************************************
%
%\section{pNets additional definitions}
%\label{secn:pNets:additional}
%
%\begin{definition}[Sorts, Holes, Leaves of pNets]
%  \begin{itemize}
%  \item  \noteSB{I think this can be lightened up a bit, since the definitions are all 
%  straightforward, whereas the notation is complex.  Maybe reformulate in words and move 
%  the formal definitions in the appendix?}
% The sort of a pNet is its signature, i.e. the set of actions it can
%perform. \noteSB{Is there any chance that, by writing assignments explicitly ($x := e$), 
%we could eliminate the need to distinguish the input variables at all? That would 
%simplify things.}\hl{In the definition of sorts, we do not need to distinguish
%input variables} (that specify the dataflow within LTSs), so for
%computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in 
%K}$ is the parallel substitution 
%operation.} to remove the
%\emph{input marker} of variables\footnote{$\overline{S}$ denotes a set of $S$.}. Formally:
%\[
%\begin{array}{l}
%\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
%x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~g,~(x_j\!:= {e}_j)^{j\in
%    J}\rangle} s'\in \to \} \\
%\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
%\overline{\pNet}\!,
%\overline{\symb{SV}}\myrangle)
%=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
%\to\alpha'\in\set{\symb{SV}}\}
%\end{array}
%\]
%
%\item
%The set of holes of a pNet is defined inductively; the sets of holes
%in a pNet node and its subnets are all disjoint:
%  \[\begin{array}{l}
%\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
%\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
%=J\uplus{\displaystyle \bigcup_{i\in 
%I}\Holes(\pNet_i)}\\
%\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
%\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  
%\Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
%\end{array}\]
%\item
%The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined 
%inductively as:
%\[\begin{array}{l}
%\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\emptyset\\%\{\mylangle S,s_0, \to\myrangle\}\\
%\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
%\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
%I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i\pNet_i \text{ is a }\pLTS\}}
%\end{array}\]
%\end{itemize}
%\end{definition}

@@

In this section condensed from
\cite[Section~4]{BarBliu15-offer-scico}, we briefly recall the syntax
and semantics of the algebras used to represent BIP interaction models
\emph{disregarding variables and data transfer}.  All the algebras are
parameterised by a set $P$ of all the ports in a given system.  The
semantics of the Algebra of Interactions $\ai(P)$ is given in terms of
sets of interactions by a function $\intsem{\cdot}: \ai(P) \rightarrow
2^{2^P}$.  The corresponding equivalence relation on $\ai(P)$ is
defined as follows: two terms $x,y \in \ai(P)$ are {\em equivalent} $x
\simeq y$ iff $\intsem{x} = \intsem{y}$.  For any other algebra
$\cA(P)$ among those appearing in this section, we define its
semantics by the function $\aisem{\cdot}: \cA(P) \rightarrow \ai(P)$.
A function $\intsem{\cdot}: \cA(P) \rightarrow 2^{2^P}$ is obtained by
composing $\aisem{\cdot}: \cA(P) \rightarrow \ai(P)$ and
$\intsem{\cdot}: \ai(P) \rightarrow 2^{2^P}$.  The axiomatisation of
$\ai(P)$ given in \cite{BliSif07-acp-emsoft} is sound and complete
with respect to $\simeq$.  Hence, for other algebras, the equivalences
induced by $\intsem{\cdot}$ and $\aisem{\cdot}$ coincide.

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.18\textwidth}
    %% \rule{\textwidth}{0.5pt}
    \centering
    \input{figures/rdv.pspdftex}
    \caption{\centering Rendezvous~$pqr$
      $\intsem{pqr} = \{pqr\}$}
    \label{fig:connectors:rdv}
  \end{subfigure}%
  \hfill %add desired spacing between images, e. g. ~, \quad, \qquad etc.
  %(or a blank line to force the subfigure onto a new line)
  \begin{subfigure}[b]{0.24\textwidth}
    %% \rule{\textwidth}{0.5pt}
    \centering
    \input{figures/broadcast.pspdftex}
    \caption{\centering Broadcast~$p'qr$
      $\intsem{p'qr} = \{p, pq, pr, pqr\}$}
    \label{fig:connectors:bdc}
  \end{subfigure}%
  \hfill %add desired spacing between images, e. g. ~, \quad, \qquad etc.
  %(or a blank line to force the subfigure onto a new line)
  \begin{subfigure}[b]{0.24\textwidth}
    %% \rule{\textwidth}{0.5pt}
    \centering
    \input{figures/atomic-bdc.pspdftex}
    \caption{\centering Atomic broadcast~$p'[qr]$
      $\intsem{p'[qr]} = \{p, pqr\}$}
    \label{fig:connectors:atomic}
  \end{subfigure}%
  \hfill %add desired spacing between images, e. g. ~, \quad, \qquad etc.
  %(or a blank line to force the subfigure onto a new line)
  \begin{subfigure}[b]{0.23\textwidth}
    %% \rule{\textwidth}{0.5pt}
    \centering
    \input{figures/causal-chain.pspdftex}
    \caption{\centering Causal chain~$p'[q'r]$
      $\intsem{p'[q'r]} = \{p, pq, pqr\}$}
    \label{fig:connectors:causal}
  \end{subfigure}%
  \caption{Basic connector examples}
  \label{fig:connectors}
\end{figure}

\section{Additional material for the theory of architectures}
\label{secn:arch:appendix}

>>>>

\newcommand{\defn}[1]{Def.~\ref{defn:#1}}
\newcommand{\defntwo}[2]{Defs~\ref{defn:#1} and \ref{defn:#2}}
\newcommand{\fig}[1]{Fig.~\ref{fig:#1}}
\newcommand{\Fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\figs}[2]{Fig.~\ref{fig:#1} and~\ref{fig:#2}}
\newcommand{\tab}[1]{Tab.~\ref{tab:#1}}
\newcommand{\eq}[1]{(\ref{eq:#1})}
\newcommand{\res}[1]{(\ref{res:#1})}
\newcommand{\ex}[1]{Ex.~\ref{ex:#1}}
\newcommand{\exs}[2]{Ex.~\ref{ex:#1} and~\ref{ex:#2}}
\newcommand{\secn}[1]{Sect.~\ref{secn:#1}}
\newcommand{\app}[1]{App.~\ref{secn:#1}}
\newcommand{\rem}[1]{Note~\ref{rem:#1}}
\newcommand{\lem}[1]{Lem.~\ref{lem:#1}}
\newcommand{\cor}[1]{Cor.~\ref{cor:#1}}
\newcommand{\thm}[1]{Th.~\ref{thm:#1}}
\newcommand{\Thm}[1]{Theorem~\ref{thm:#1}}
\newcommand{\axs}[1]{Ax.~\ref{ax:#1}}
% \newcommand{\ax}[2]{\ref{ax:#1}.\ref{ax:#1:#2}}
\newcommand{\ax}[1]{Ax.~\ref{ax:#1}}
\newcommand{\prop}[1]{Prop.~\ref{prop:#1}}
\newcommand{\alg}[1]{Alg.~\ref{alg:#1}}
\newcommand{\asmp}[1]{Ass.~\ref{asmp:#1}}

@@

\addSB{%
%
\Thm{combining} implies that safe BIP systems can be designed
\emph{compositionally}.  Indeed, it is sufficient to verify that
1)~the applied architectures do enforce their characteristic
properties and 2)~that they are pairwise upwards compatible.  To
a large extent, item~2, \ie verification of the upwards
compatibility, can be carried out syntactically by analysing the
structure of the connectors defining the interaction models:
maximal progress is mostly relevant for connectors involving
triggers; whenever a trigger port is not common to both
architectures, upwards \emph{in}compatibility cannot arise.  The
next section is devoted to the encoding of architectures into
pNets, which addresses item~1 by symbolic verification.
%
}

@@

The encoding of the interaction model is based on its representation
as a set of connectors. %% \noteSB{%
%
%%   A legitimate question is whether we actually need to do this,
%%   instead of listing explicitly the individual interactions, then
%%   associating a synchronisation vector to each one of them?  One of
%%   the factors is the encoding pNets$\rightarrow$SAT: is it better to
%%   have more or fewer SVs if the price is additional Boolean variables?
%%   The other factor might be the facility of maximal progress
%%   encoding\mdash TBC.  Traceability.  Anything else?\newline
%%   \hl{UPDATE: Maximal progress encoding requires this!}
%% %
%% }
Indeed, as illustrated by the Failure Monitor architecture in
\fig{schema:ArchFailure:BIP}, each connector can define several
allowed interactions, depending on its hierarchical structure and the
use of synchrons and triggers.

@@

\paragraph{Encoding of the maximal progress priority model}
We only present the key idea, which consists in
introducing an additional Boolean variable, for each port, for which we
have introduced one in $\nopri[A, \partition]$.  Intuitively, 
the Boolean
variables introduced for the encoding of interaction models
determine whether it is the original transition
labeled by the port that is executed (\true), or rather the corresponding
self-loop, introduced by the encoding (\false).  The new variables
determine whether \emph{there is an original transition labelled by
  $p$ that could be executed from the same state}, \ie[,] with $b_p$
the variable introduced above for the encoding without maximal
progress, $q \goesto{p(\true, b_p)} q'$ iff $\exists q'': q
\goesto{p(b_p)} q''$ with $b_p = \true$ in $\nopri[A, \partition]$.
Then, in the SV guard, we have to check whether \emph{all ports
  leading to $p$ in the causal tree $\tau(x)$ can be fired} (see
\app{transformations}).  If so, then $p$ must be fired, \ie
$p(\false)$ must be blocked.
%% This is pretty much straightforward, but
%% care must be taken when doing this in the general case, since causal
%% interaction trees can get pretty tricky due to $\oplus$ (see
%% \app{trees}).}
%****************************************************************
%****************************************************************

@@

%% \section{Case study}
%% \label{secn:case-study}

%% %****************************************************************

@@

%% %****************************************************************

%% \subsection{Composition of architectures}
%% \label{secn:arch:composition}

%% We now consider a system comprising two components $B_1$ and $B_2$
%% with the corresponding interfaces $\tuple{V_i, P_i,
%%   \export[i]}_{i=1,2}$, such that $\listset{\PortFail_i,
%%   \PortResume_i} \subseteq P_i$, for $i = 1,2$.

%% Assuming that the associated system requirements comprise the
%% capability of monitoring the failure events corresponding to ports
%% $\PortFail_1$ and $\PortFail_2$ of the two components, we would like
%% to apply two instances of the Failure Monitor architecture.  However,
%% we impose an additional constraint: only one timer coordinator is
%% allowed, for example because it must eventually be implemented by a
%% hardware component.

%% We consider two architecture instances $A_i = \tuple{\cC_i, V_{A_i},
%%   P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$, with all their
%% constituting elements cloned from the Failure Monitor architecture of
%% the previous examples while substituting each entity $X$ by $X^i$.
%% For instance, the initialisation of the $\mathit{zone}$ variable is
%% transformed into $\IntervalInit[1]$ and $\IntervalInit[2]$,
%% respectively.  The only exception to this cloning procedure are the
%% sets of coordinating components: $\cC^i = \listset{\NameTimer,
%%   \NameCtrl^i}$, \ie the $\NameTimer$ component is shared, while
%% components $\NameCtrl^1$ and $\NameCtrl^2$ are obtained by making two
%% copies of $\NameCtrl$ as above.

%% In order to apply both architectures, we must verify that they are
%% upwards compatible and compute the combined interaction model $\Gamma$
%% in $A_1 \arcomp A_2 = \tuple{\cC_1 \cup \cC_2, V_{A_1} \cup V_{A_2},
%%   P_{A_1} \cup P_{A_2}, \export[A_1] \cup \export[A_2], \Gamma}$
%% (see \defn{arch:composition}).

%% \todoSBin{Complete this section}

@@

This section presents some material that has already been published in earlier work but is essential for understanding the encoding in \secn{encoding}.
It is condensed from
\cite[Section~4]{BarBliu15-offer-scico} and recalls briefly the syntax
and semantics of the algebras used to represent BIP interaction models
\emph{disregarding variables and data transfer}.

All the algebras are
parameterised by a set $P$ of all the ports in a given system.  The
semantics of the Algebra of Interactions $\ai(P)$ is given in terms of
sets of interactions by a function $\intsem{\cdot}: \ai(P) \rightarrow
2^{2^P}$.  The corresponding equivalence relation on $\ai(P)$ is
defined as follows: two terms $x,y \in \ai(P)$ are {\em equivalent} $x
\simeq y$ iff $\intsem{x} = \intsem{y}$.  For any other algebra
$\cA(P)$ among those appearing in this section, we define its
semantics by the function $\aisem{\cdot}: \cA(P) \rightarrow \ai(P)$.
A function $\intsem{\cdot}: \cA(P) \rightarrow 2^{2^P}$ is obtained by
composing $\aisem{\cdot}: \cA(P) \rightarrow \ai(P)$ and
$\intsem{\cdot}: \ai(P) \rightarrow 2^{2^P}$.  The axiomatisation of
$\ai(P)$ given in \cite{BliSif07-acp-emsoft} is sound and complete
with respect to $\simeq$.  Hence, for other algebras, the equivalences
induced by $\intsem{\cdot}$ and $\aisem{\cdot}$ coincide.

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.18\textwidth}
    %% \rule{\textwidth}{0.5pt}
    \centering
    \input{figures/rdv.pspdftex}
    \caption{\centering Rendezvous~$pqr$
      $\intsem{pqr} = \{pqr\}$}
    \label{fig:connectors:rdv}
  \end{subfigure}%
  \hfill %add desired spacing between images, e. g. ~, \quad, \qquad etc.
  %(or a blank line to force the subfigure onto a new line)
  \begin{subfigure}[b]{0.24\textwidth}
    %% \rule{\textwidth}{0.5pt}
    \centering
    \input{figures/broadcast.pspdftex}
    \caption{\centering Broadcast~$p'qr$
      $\intsem{p'qr} = \{p, pq, pr, pqr\}$}
    \label{fig:connectors:bdc}
  \end{subfigure}%
  \hfill %add desired spacing between images, e. g. ~, \quad, \qquad etc.
  %(or a blank line to force the subfigure onto a new line)
  \begin{subfigure}[b]{0.24\textwidth}
    %% \rule{\textwidth}{0.5pt}
    \centering
    \input{figures/atomic-bdc.pspdftex}
    \caption{\centering Atomic broadcast~$p'[qr]$
      $\intsem{p'[qr]} = \{p, pqr\}$}
    \label{fig:connectors:atomic}
  \end{subfigure}%
  \hfill %add desired spacing between images, e. g. ~, \quad, \qquad etc.
  %(or a blank line to force the subfigure onto a new line)
  \begin{subfigure}[b]{0.23\textwidth}
    %% \rule{\textwidth}{0.5pt}
    \centering
    \input{figures/causal-chain.pspdftex}
    \caption{\centering Causal chain~$p'[q'r]$
      $\intsem{p'[q'r]} = \{p, pq, pqr\}$}
    \label{fig:connectors:causal}
  \end{subfigure}%
  \caption{Basic connector examples}
  \label{fig:connectors}
\end{figure}

\section{Additional definitions for the theory of architectures}
\label{secn:arch:appendix}

@@

%*********************************************************************
%*********************************************************************
%
%%\section{pNets additional definitions}
%\label{secn:pNets:additional}
%
%\begin{definition}[Sorts, Holes, Leaves of pNets]
%  \begin{itemize}
%  \item  \noteSB{I think this can be lightened up a bit, since the definitions are all 
%  straightforward, whereas the notation is complex.  Maybe reformulate in words and move 
%  the formal definitions in the appendix?}
% The sort of a pNet is its signature, i.e. the set of actions it can
%perform. \noteSB{Is there any chance that, by writing assignments explicitly ($x := e$), 
%we could eliminate the need to distinguish the input variables at all? That would 
%simplify things.}\hl{In the definition of sorts, we do not need to distinguish
%input variables} (that specify the dataflow within LTSs), so for
%computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in 
%K}$ is the parallel substitution 
%operation.} to remove the
%\emph{input marker} of variables\footnote{$\overline{S}$ denotes a set of $S$.}. Formally:
%\[
%\begin{array}{l}
%\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
%x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~g,~(x_j\!:= {e}_j)^{j\in
%    J}\rangle} s'\in \to \} \\
%\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
%\overline{\pNet}\!,
%\overline{\symb{SV}}\myrangle)
%=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
%\to\alpha'\in\set{\symb{SV}}\}
%\end{array}
%\]
%
%\item
%The set of holes of a pNet is defined inductively; the sets of holes
%in a pNet node and its subnets are all disjoint:
%  \[\begin{array}{l}
%\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
%\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
%=J\uplus{\displaystyle \bigcup_{i\in 
%I}\Holes(\pNet_i)}\\
%\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
%\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  
%\Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
%\end{array}\]
%\item
%The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined 
%inductively as:
%\[\begin{array}{l}
%\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\emptyset\\%\{\mylangle S,s_0, \to\myrangle\}\\
%\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
%\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
%I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i\pNet_i \text{ is a }\pLTS\}}
%\end{array}\]
%\end{itemize}
%\end{definition}

@@
